The implications of the COVID-19 epidemic has meant that we are limited in our ability to reach any concrete measured conclusion, regarding of proposed solution.
Therefore we will try to make our conclusion on the basics of our tacit knowledge from developing software, both as students of Aalborg University, but also as business owners and employees in software development teams.
Since this project group consists of people that besides studying at the University of Aalborg also work in software development, either as owners or employees of companies.

It is important for us to disclaim that all conclusions will be based on our needs and understanding, therefore they might not hold if one were to conduct a real usability test and cross-check our conclusion.
We uphold the right to reevaluate our conclusion if a usability test is ever to be conducted.

We believe that we have built a solution that can ease the communication pains highlighted in the study by Hoda, Noble, and Marshall \cite{Hoda2011TheIO}. 
Our solution allows the customer to create specifications from their domain and thereby allowing them to create specifications "in the moment" that they realize they need for functionality.
We also believe that our solution is beneficial for the developers since it can automatically convert specifications into executable tests.
This will allow the developers to assert whether their implementation lives up to the expectations of the customer within seconds.

Our solutions have some obvious limitations, at this stage the solution does not offer many UI-elements and it does not offer any interaction or behavior-based specifications.
This renders the solution unusable for industry use, but we have managed to build an architecture that is highly modulized and expandable, therefore we find it trivial to include more UI-elements and manageable to introduce interaction and behavior specifications.

The Design by Contract methodology showed very usefully in this solution, we believe that our solution embodies the Design by Contract methodology but lacks very important details.
At the current stage of the solutions there is no real method for defining pre-conditions and invariants, which is obvious violence of the Design by Contract method.
We also believe that our solutions have been too hard coupled to the Flutter environment, and that is a problem for general use. 
We, therefore, conclude that we did not manage to implement a generalized interface between the "What You See Is What You Get"-editor and the Test Generator.
We should have to build a more formal interface that was Design by Contract oriented instead of Flutter orientated.